---
title: "Assignment 9"
author: "Kyle Bradshaw"
date: "3/27/2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## A run down of the data
```{r}
library(tidyverse)
library(modelr)
library(easystats)
library(GGally)
```
After loading the packages we open and do a quick analysis of the data set.
```{r}
df <- read_csv("../../Data/GradSchool_Admissions.csv")
glimpse(df)
```
We are wanting to predict the admitance rate of students based on their gpa,gre, and the rank of the univerity where they studied for their undergraduate degree. For ease of analysis admitance will be changed from bionary to logical.

```{r}
df <- df %>% 
  mutate(admit=case_when(admit == 1 ~ TRUE,
                         admit == 0 ~ FALSE),
         rank=factor(rank))

df %>% glimpse()
```
## Model Selection

We are going to compare all possible graphs to derive the potential models.

```{r}
ggpairs(df)
```

We then generate the following models trying to predict the admitance against various influencing factors.

```{r}
mod1 <- glm(data=df,
            formula = admit ~ gre + gpa + rank,
            family = "binomial")

mod2 <- glm(data=df,
            formula = admit ~ gre + gpa,
            family = "binomial")

mod3 <- glm(data=df,
            formula = admit ~ gre,
            family = "binomial")

mod4 <- glm(data=df,
            formula = admit ~ gpa + rank,
            family = "binomial")

mod5 <- glm(data=df,
            formula = admit ~ rank,
            family = "binomial")

mod6 <- glm(data=df,
            formula = admit ~ gre + rank,
            family = "binomial")

mod7 <- glm(data=df,
            formula = admit ~ gpa,
            family = "binomial")

comps <- compare_performance(mod1,mod2,mod3,mod4,mod5,mod6,mod7,
                             rank=TRUE)
comps
```
We then compare all of the models graphically.
```{r}
comps %>% plot()
```

It is seen that the best prediction comes from model 1 with the combination of gpa, gre, and the universities rank. We then generate a few models to illustrate the prediction accuracy.

```{r}
add_predictions(df,mod1,type = "response") %>% 
  ggplot(aes(x=gpa,y=pred,color=rank)) +
  geom_smooth() +
  labs(title = "acceptance prediction vs gpa score",
       subtitle = "separated based on univerity ranckings")
```
```{r}
add_predictions(df,mod1,type = "response") %>% 
  ggplot(aes(x=gre,y=pred,color=rank)) +
  geom_smooth() +
  labs(title = "acceptance prediction vs gre score",
       subtitle = "separated based on univerity ranckings")
```

